\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}. The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow. \red{(???? THE TWO PAPERS ARE EXPERIMENTAL ... THIS SENTENCE DOES NOT MAKE ANY SENSE ... PLEASE READ IT THROUGH !!)}

%Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. 
\red{(PLEASE REVISE THE PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}
In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations. Following a different set-up the idea is to validate the existance of cross flow and along with another region of different permeability.There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop. The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.

>>>>

Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}. The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow. \red{(???? THESE TWO PAPERS ARE EXPERIMENTAL ... THIS LAST SENTENCE DOES NOT MAKE ANY SENSE ... PLEASE READ IT THROUGH AND ADDRESS MY PREVIOUS COMMENT ...!!)}

%Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. 
\red{(PLEASE REVISE THIS PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS WRT FIG 5 AND FIG 4 !!!! ....)}
In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations. Following a different set-up the idea is to validate the existance of cross flow and along with another region of different permeability.There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop. The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
